Immigration and Onshoring of High-Impact R&D

### 2020-11-12 Presentations/paper_outline.Rmd
update of training data for models with 9200 additional names (ready for training the models).

---
title: "Immigration and Onshoring of High-Impact R&D"
subtitle: "Research Outline"
author: "Matthias Niggli"
date: "`r Sys.Date()`"
# bibliography: bibliography.bib # throws an error with this markdown version because of the .bib file.
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("tensorflow")
library("keras")
library("reticulate")

if(file.exists("/scicore/home/weder/nigmat01/inventor_migration")) {
        PATH <- "/scicore/home/weder/nigmat01/inventor_migration"}else{
                PATH <- "C:/Users/Matthias/Documents/GithubRepos/inventor_migration"}

```

@@

#### load data -----------------------------------------------------
inv_dat <- readRDS(paste0(PATH, "/Data/patent_data/inventor_origin.rds"))

#### load the classification model  -------------------------------------------
origin_model <- load_model_hdf5(paste0(PATH, "/Data/classification_model/origin_class_model.h5"))
origin_model <- load_model_hdf5(paste0(PATH, "/Data/classification_model/origin_class_model.h5"))
origin_model <- load_model_hdf5(paste0(PATH, "/Data/classification_model/origin_class_model.h5"))

@@

## function to encode names
source(paste0(PATH, "/Code/model_training/names_encoding_function.R"))

@@

        p <- ggplot(plot_dat, aes(x = p_year, y = share))+
                facet_wrap(.~ tech_field)+
                geom_line()+
                labs(y = "Share of domestic origin", 
                     x = "Year", title = paste0(" Share of ", DOMESTIC_ORIGIN, " origin in ",
                                                COUNTRY, " (by technological field)"))
        return(p)
}
```

@@

```{r}
exp_name = encode_chars(names = "rolf weder", 
                        char_dict = c(letters, " ", "END"), 
                        seq_max = 10, n_chars = 28)
exp_name[1, ,]
```

@@

```{r, echo=FALSE, warnings=FALSE, message=FALSE, fig.width=10, fig.height=4, fig.align="center"}
COUNTRIES <- c("US", "CN", "JP", "KR", "GB", "FR", "DE", "IT")
DOMESTIC_ORIGIN <- c("AngloSaxon", "China", "Japan", "Korea", 
                     "AngloSaxon", "French", "German", "Italian")

# SHOW PLOT FOR CLASSIFICATION AS A ROBUSTNESS CHECK
```

>>>>

---
title: "Immigration and Onshoring of High-Impact R&D"
subtitle: "Research Outline"
author: "Matthias Niggli"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("tensorflow")
library("keras")
library("reticulate")
```

@@

#### load data -----------------------------------------------------
inv_dat <- readRDS("/scicore/home/weder/nigmat01/inventor_migration/Data/patent_data/inventor_origin.rds")

#### load the classification model  -------------------------------------------
origin_model <- load_model_hdf5("/scicore/home/weder/nigmat01/inventor_migration/Data/classification_model/origin_class_model.h5")
origin_model <- load_model_hdf5("/scicore/home/weder/nigmat01/inventor_migration/Data/classification_model/origin_class_model.h5")
origin_model <- load_model_hdf5("/scicore/home/weder/nigmat01/inventor_migration/Data/classification_model/origin_class_model.h5")

@@

## function to encode names
source("/scicore/home/weder/nigmat01/inventor_migration/Code/model_training/names_encoding_function.R")

@@

        p <- ggplot(plot_dat, aes(x = p_year, y = share))+
                facet_wrap(.~ tech_field)+
                guides(NULL)+
                geom_line(aes(aes(color = tech_field)))+
                labs(y = "Share of domestic origin", 
                     x = "Year", title = paste0(" Share of ", DOMESTIC_ORIGIN, " origin in ",
                                                COUNTRY, " (by technological field)"))
        return(p)
}
```

@@

```{r, echo=FALSE}
exp_name = encode_chars(names = "rolf weder", 
                        char_dict = c(letters, " ", "END"), 
                        seq_max = 10, n_chars = 28)
exp_name[1, ,]
```

@@
